Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-07-12 analysis/paper/sim_survey_paper.Rmd
Work up two plot functions for a plot for the paper
Resort to static plots and add first figure to paper

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "../..")
```

```{r data, include = FALSE}
load("analysis/cod_sim_exports/2018-07-07_test/test_output.RData")
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      dev = "png",
                      dpi = 300)
knitr::opts_knit$set(root.dir = "../..")
```

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
load("analysis/cod_sim_exports/2018-07-07_test/test_output.RData")
```

@@

# Figures

```{r ex_fig, fig.height = 3.8, fig.width = 8.5}

which_year <- 7
which_sim <- 4

sp_N_tot <- sim$sp_I[year == which_year & sim == which_sim, list(N = sum(I)), by = c("year", "cell")]
xyz <- merge(sim$grid_xy, sp_N_tot, by = "cell")
size <- unique(diff(pretty(xyz$N, 25)))

sp_strat <- raster::rasterToPolygons(sim$grid$strat, dissolve = TRUE)
df_strat <- suppressWarnings(fortify(sp_strat) %>% group_by(group))

r <- raster::rasterFromXYZ(xyz[, c("x", "y", "N")])
l <- rasterToContour(r, levels = pretty(xyz$N, 20))
df_lines <- suppressWarnings(fortify(l))
levels <- as.numeric(as.character(l$level))
levels <- paste0(levels / 1000, "k")
labs <- levels
labs[seq_along(labs) %% 2 == 0] <- ""
levels <- factor(levels, levels = levels)
names(levels) <- rownames(as.data.frame(l))
df_lines$level <- levels[df_lines$id]

abun_plot <- ggplot() +
  geom_path(data = df_strat, aes(x = long, y = lat, group = group), 
            color = "grey", size = 0.05) +
  geom_path(data = df_lines, aes(x = long, y = lat, group = group, color = level),
            size = 0.3) +
  scale_color_viridis(labels = labs, discrete = TRUE, name = "N") + 
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  coord_equal() +
  theme_void() + guides(color = guide_legend(keywidth = 0.4, keyheight = 0.25, 
                                             default.unit = "cm", ncol = 1)) +
  theme(legend.justification = c(0, 1),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))

setdet <- sim$setdet
setdet <- setdet[setdet$year == which_year & setdet$sim == which_sim, ]

set_plot <- ggplot() +
  geom_path(data = df_strat, aes(x = long, y = lat, group = group), 
            color = "grey", size = 0.05) +
  geom_point(data = setdet, aes(x = x, y = y, size = n, color = n), alpha = 0.8) +
  scale_size_area(name = "   n", max_size = 10, breaks = pretty(setdet$n, 8)) +
  scale_color_viridis(name = "   n", breaks = pretty(setdet$n, 8)) + 
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  coord_equal() +
  theme_void() + guides(color = guide_legend(keywidth = 0.4, keyheight = 0.2, default.unit = "cm")) +
  theme(legend.justification = c(0, 1),
        plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm"))

p <- cowplot::plot_grid(abun_plot, set_plot, labels = c("a)", "b)"), align = "hv",
                   label_fontface = "plain")
cowplot::save_plot(plot = p, filename = "analysis/paper/figures/abun_and_sets_example.pdf",
                   base_height = 3.8, base_width = 8.5)
p

```
